\chapter*{Preface}
\vspace{-12 pt}
This project aims at the design of an autonomous vehicle prototype, able to run and follow a predefined route, in the perspective of using it as a lawn mower.

The hereby report has been written by a group of students on fifth semester in ``Electronics and IT'' at Aalborg University.\\
The reader should have a basic knowledge and understanding in electronics engineering, and more specifically in modelling and control, communication in electronic systems and signal processing. Specific knowledge related to the implemented controllers, communication protocol and digital filter will be described in more details. Code for the implementation of the prototype is written in C, Arduino-specific C\texttt{++} and in C\texttt{\#}. It is assumed that the reader is able to comprehend these programming languages.

Special thanks are addressed to Rasmus Gundorff Sæderup for his contribution in taking professional looking pictures of the vehicle, Associate Professor Henrik Schiøler for guidance on the GoT system, and to Associate Professor Jens Dalsgaard Nielsen for the support he brought the group on his kernel. Final thanks are for the group's supervisors Tom Søndergaard Pedersen and Rasmus Pedersen and their guidance throughout the semester.

\textbf{Reading Instructions}
\vspace{-10 pt}
\begin{itemize}
\item[-] This report is organized in three parts. The first part describes the design process of the wanted prototype. The second one covers the actual implementation choices made to fulfill the requirements. In the last part, the prototype's characteristics are actually tested. From this, a conclusion on the project is made as well as a discussion on potential improvements of the prototype.
\item[-] On the attached CD, the following content can be found: main project code, code, data and Matlab scripts used in the tests, datasheets on components and standards used, schematics, sources used in the project which are not freely available.
\end{itemize}
%
Text by:\\
\vspace{-12 pt}
\begin{table}[H]
	\centering
		\begin{tabular}{c c c}
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Amalie V. Petersen			& \phantom{cookies} & Julien Br\'ehin		\\
			% &&
			&&\\
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Mads R. Gotthardsen			& \phantom{cookies} & Niels Skov Vestergaard		\\
			% &&\\
			&&\\
	    	\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Romaric Destremau 					& \phantom{cookies} & Thomas Rasmussen 			\\			
		\end{tabular}
\end{table}