%-- Section : Satellite vs GoT --%
\section{Satellite based positioning systems vs GoT}
\todo{Wrong reasons for GPS vs GoT, elaborated below}
The reasons why satellite positioning system probably souldn't be used for autonomous systems like a lawn mower are mainly related to accuracy-over-price ratios and to energy consumption.\todo{--To be reviewed again-- GPS uses very little power -> depending on the accuracy needed...}\\\\
Indeed, these kinds of system like GPS or GLONASS would require a dedicated chip to put on the final system. The problem then would be the lack of precision. Although, there are some cheap standard GPS chips (around USD 10), these only reach around 1 meter of precision in the most ideal situations \cite{GPSUSWebsiteAccuracy,Miller}. \\
On the other hand, the best GPS chips can achieve precisions up to a few millimeters \cite{GPSUSWebsiteAccuracy} when combined with different augmentation systems (algortihms for instance), but they end up being highly expensive (usually thousands of dollars). They are not generally intended for public use.
\todo{--To be reviewed again-- Only applies to cheap solutions, differential GPS can go to mm level, but is extremely expensive. This is what we are trying to replace with GoT, as it is a lot cheaper than diff-GPS} \\\\
%
Moreover, if we add up the slow bit rates satellites can achieve, the signal amplifiers on the receiver, plus all the position calculations and potential augmentation systems, the total energy consumption would quickly rise, \todo{--To be reviewed again-- nope, it's just a radio receiver, uses almost no power} thus reducing the lawn mower autonomy, which is not desirable.\\\\
%
Indeed, the design of a product has no real value if no one is interested in using it. This is why choices made during this project have to be made in accordance with the final user's expectations.